\section{Introduction}

Low-resource glyph and grouped recognition pipelines often collapse uncertainty too early. A common pattern is image to top-one transcript to higher-level reasoning. In handwriting and sequence recognition, that collapse can happen before lexicons, language models, or grouped constraints have a chance to use the alternatives that were locally plausible in the first place~\cite{plamondon2000handwriting,graves2006ctc,scheidl2018wordbeam}. The cost is highest under ambiguity, where grouped labels are scarce and local visual evidence is weak.

Modern calibration and conformal prediction make it easier to reason about local confidence and prediction sets~\cite{guo2017calibration,angelopoulos2021conformal}, but they do not by themselves explain whether rescued alternatives survive long enough to matter at grouped or downstream levels. That missing link motivates this paper.

We study a bounded version of the problem. We do not ask whether preserved uncertainty solves decipherment, semantic recovery, or manuscript interpretation. We ask when preserved uncertainty becomes useful at higher levels of inference, and when it does not.

Our central claim is narrow and evidence-bound: preserved transcription uncertainty improves real grouped top-k recovery across two token-aligned corpora, but higher-level propagation is support-gated. Grouped rescue predicts downstream success only in specific support regimes, and exact real downstream gains remain selective rather than replicated.

The paper is built around three linked results. First, it extends earlier symbol-level uncertainty findings into grouped and downstream settings using synthetic-from-real tasks on Omniglot, scikit-learn Digits, and Kuzushiji-49. Second, it establishes a replicated real grouped result on Historical Newspapers and ScaDS.AI grouped words. Third, it replaces a coverage-limited real downstream task with a better-covered alternative and then explains why downstream propagation still remains mixed.

The contribution is therefore analytical rather than architectural. The evaluation includes beam, trigram, conformal, and CRF-style decoders, but the main paper insight is not that another decoder wins universally. The more useful finding is that grouped rescue is real, measurable, and replicated, while downstream propagation depends on support conditions instead of occurring automatically.
